What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-19 lda-paper.tex
- [X] Address how we found the purpose of commits You say that you tries to identify the purpose of the topic. How did you do it? Was it by looking at the commit messages, or just by reading the list of words? Did you check your assumptions?

We found there
were common words across topic clusters, such as \emph{diffs},
\emph{annotate} and \emph{history}; since these words occur so often
in the MySQL 3.23 messages, we probably should be viewed as stop
words. There were notable transitional topics such as in the first
window the word \emph{BitKeeper} appears because MySQL adopted
Bitkeeper for their source control system yet in the following windows
there were no mentions of BitKeeper. \emph{RENAME} also only appeared
once in the first window and never again. Per each topic we tried to
identify the purpose of the topic; to our surprise we found that even
with only a little familiarity with the code base that naming the
topic was straightforward.

>>>>

We found there were common words across topic clusters, such as
\emph{diffs}, \emph{annotate} and \emph{history}; since these words
occur so often in the MySQL 3.23 messages, we probably should be
viewed as stop words. There were notable transitional topics such as
in the first window the word \emph{BitKeeper} appears because MySQL
adopted Bitkeeper for their source control system yet in the following
windows there were no mentions of BitKeeper. \emph{RENAME} also only
appeared once in the first window and never again. Per each topic we
tried to identify the purpose of the topic; to our surprise we found
that even with only a little familiarity with the code base that
naming the topic was straightforward. To find the purpose of a commit
we looked at the most frequent words in the word distribution of the
topic and tried to summarize the topic, then we looked into the
commits related to that topic to investigate if we were correct; since
the commit messages and the word distribution share the same words the
purpose extracted from commit comments was usually accurate.
